### 2024-09-25 manuscript.tex
Restructuring methods

The Automatic Lidar and Ceilometer Framework (ALCF) is a ground-based lidar
simulator and a tool for processing observed lidar data, supporting various
instruments and models. It performs radiative transfer calculations to derive
equivalent lidar AVBC in an atmospheric model, which can then be compared with
observed AVBC \citep{kuma2021}. For this purpose, it takes atmospheric fields
of cloud fraction, liquid and ice mass mixing ratio, temperature, and pressure
fields as an input and can be run offline (on the model output rather than
inside the model code). The lidar simulator in the ALCF is based on the
instrument simulator Cloud Feedback Model Intercomparison Project (CFMIP)
Observation Simulator Package (COSP) \citep{bodas-salcedo2011}.  After AVBC is
calculated, a cloud mask, cloud occurrence by height, and the total cloud
fraction are determined. The ALCF has already been used by several research
teams for model and reanalysis evaluation
\citep{kuma2020,kremser2021,guyot2022,pei2023,whitehead2023,mcdonald2024}.
Absolute calibration of the observed backscatter was performed by comparing the
measured clear-sky molecular backscatter statistically with simulated clear-sky
molecular backscatter. AVBC is resampled to 5 min temporal resolution and 50 m
vertical resolution to increase signal-to-noise ratio, while having enough
resolution to detect small-scale cloud variability. Noise standard deviation is
calculated from AVBC at the highest range, where no clouds are expected.  A
cloud mask is calculated from AVBC using a fixed threshold of $\mathrm{2\times
10^{-6} m^{-1}sr^{-1}}$ after subtracting 5 standard deviations of range-scale
noise. Fig. \ref{fig:example}b shows an example of simulated Vaisala CL51
backscatter from ERA5 data, corresponding to a day of measurements by the
instrument on the PS81/3 voyage.

@@

A coupled (atmosphere--ocean) GSRM version of the ICON model is in development
by the nextGEMS project \citep{hohenegger2023}. nextGEMS has so far produced
four cycles of model runs. In our research, we used a Cycle 3 run
\emph{ngc3028} produced in 2023 \citep{nextgems2023a,nextgems2023b}. We could
not use Cycle 4 due to the unavailability of the necessary variables. The
horizontal resolution of ngc3028 is about 5 km.  Unlike current general
circulation models (GCMs), the strom-resolving version of ICON does not use
convective and cloud parameterisation but relies on explicit simulation of
convection and clouds on the model grid. While this makes the code development
simpler without having to rely on uncertain parameterisations, it can miss
smaller-scale clouds below the grid resolution.  Turbulence and cloud
microphysics are still parameterised in this model. In our analysis, we used
four years of coupled simulation output between years 2021 and 2024
(inclusive). Because the model is free-running, weather and climate
oscillations (such as the El Niño--Southern Oscillation) are not expected to be
equivalent to reality at the same time and place. To compare with observations
taken during different years (2010--2021, inclusive), we compared the model
output with observations at the same time of year and geographical location.

ICON is a very versatile model, allowing for simulations ranging from
coarse-resolution ESM simulations, GSRM simulations, limited area model (LAM)
simulations, to large eddy simulations (LES), for both weather prediction and
climate projections.

ICON uses the atmospheric component ICON-A \citep{giorgetta2018}, whose physics
is derived from ECHAM6 \citep{stevens2013}, and the ocean component ICON-O
\citep{korn2022}.

Earlier runs of the GSRM ICON from DYAMOND were evaluated by
\cite{mauritsen2022}.

@@

The Modern-Era Retrospective analysis for Research and Applications, Version 2
(MERRA-2) is a reanalysis produced by the Global Modeling and Assimilation
Office at the NASA Goddard Space Flight Center \citep{gelaro2017}.  It uses
version 5.12.4 of the Goddard Earth Observing System (GEOS) atmospheric model
\citep{rienecker2008,molod2015}. The reanalysis output analysed here is
available at a spatial resolution of 0.5° in latitude and 0.625° in longitude,
which is about 56 km in the North--South direction and 35 km in the East--West
direction at 60°S. The number of vertical model levels is 72, which we
interpolate to height levels as needed. In our analysis we use the following
products: 1-hourly instantaneous 2D single-level diagnostics (M2I1NXASM) for
2-m temperature and humidity; 3-hourly instantaneous 3D assimilated
meteorological fields (M2I3NVASM) for cloud quantities, pressure, and
temperature; 1-hourly average 2D surface flux diagnostics (M2T1NXFLX) for
precipitation and sea ice; and 1-hourly average 2D radiation diagnostics
(M2T1NXRAD) for radiation quantities \citep{merra2}.

@@

ERA5 \citep{era5} is a reanalysis produced by the European Centre for
Medium-Range Weather Forecasts (ECMWF). It is based on a numerical weather
prediction (NWP) model Integrated Forecast System (IFS) version CY41R2.  The
horizontal resolution is 0.25° in latitude and longitude, which is about 28 km
in the North--South direction and 14 km in the East--West direction at 60°S.
Internally, the model uses 137 vertical levels. In our analysis we use output
at one hourly instantaeous time intervals, except for radiation quantities,
which are accumulations (from these we calculate daily means).
Vertically-resolved quantities are made available on 37 pressure levels. We
interpolate these quantities to height levels as needed.

@@

\subsection{Cyclone tracking}

\subsection{Cloud occurrence by stability}

We partitioned our data into two subsets by stability. We determined this by
calculating lower tropospheric stability (LTS) as the difference between the
potential temperature at 700 hPa and the surface.  Based on a histogram of LTS
in ERA5 and MERRA-2 calculated at all voyage tracks and stations (Fig.
\ref{fig:lts}), we determined a dividing threshold of 12 K for relatively
unstable (< 12 K) and relatively stable (>= 12 K) conditions.

@@

\subsection{Data processing}

The radiation calculations were done in such a way that they always represent
averages of daily means. This is done in order to be consistent with the CERES
SYN1deg data, which are expressed as daily means. Therefore, for every
instantaneous profile in the simulated lidar data is assigned a daily mean
radiation value corresponding to the day (in the Coordinated Universal Time;
UTC). In turn, the average radiation during the entire voyage or station
measurement is calculated as the average of the profile values. In the observed
lidar data, the daily mean radiation value is taken from the spatially and
temporally co-located CERES SYN1deg data for the day (in UTC). The voyage or
station measurement average is calculated in the same way.

>>>>

The Automatic Lidar and Ceilometer Framework (ALCF) is a ground-based lidar
simulator and a tool for processing observed lidar data, supporting various
instruments and models. It performs radiative transfer calculations to derive
equivalent lidar AVBC in an atmospheric model, which can then be compared with
observed AVBC \citep{kuma2021}. For this purpose, it takes atmospheric fields
of cloud fraction, liquid and ice mass mixing ratio, temperature, and pressure
fields as an input and can be run offline (on the model output rather than
inside the model code). The lidar simulator in the ALCF is based on the
instrument simulator Cloud Feedback Model Intercomparison Project (CFMIP)
Observation Simulator Package (COSP) \citep{bodas-salcedo2011}.  After AVBC is
calculated, a cloud mask, cloud occurrence by height, and the total cloud
fraction are determined. The ALCF has already been used by several research
teams for model and reanalysis evaluation
\citep{kuma2020,kremser2021,guyot2022,pei2023,whitehead2023,mcdonald2024}.

Absolute calibration of the observed backscatter was performed by comparing the
measured clear-sky molecular backscatter statistically with simulated clear-sky
molecular backscatter. AVBC is resampled to 5 min temporal resolution and 50 m
vertical resolution to increase signal-to-noise ratio, while having enough
resolution to detect small-scale cloud variability. Noise standard deviation is
calculated from AVBC at the highest range, where no clouds are expected.  A
cloud mask is calculated from AVBC using a fixed threshold of $\mathrm{2\times
10^{-6} m^{-1}sr^{-1}}$ after subtracting 5 standard deviations of range-scale
noise. Fig. \ref{fig:example}b shows an example of simulated Vaisala CL51
backscatter from ERA5 data, corresponding to a day of measurements by the
instrument on the PS81/3 voyage.

@@

A coupled (atmosphere--ocean) GSRM version of the ICON model is in development
by the nextGEMS project \citep{hohenegger2023}. ICON is a very versatile model,
allowing for simulations ranging from coarse-resolution ESM simulations, GSRM
simulations, limited area model (LAM) simulations, to large eddy simulations
(LES), for both weather prediction and climate projections. ICON uses the
atmospheric component ICON-A \citep{giorgetta2018}, whose physics is derived
from ECHAM6 \citep{stevens2013}, and the ocean component ICON-O
\citep{korn2022}. Earlier runs of the GSRM ICON from DYAMOND were evaluated by
\cite{mauritsen2022}.

Here, we use a free running (i.e. \emph{not} nudged or using prescribed SST)
coupled GSRM simulation made for the purpse of climate projection.  nextGEMS
has so far produced four cycles of model runs. We used a Cycle 3 run
\emph{ngc3028} produced in 2023 \citep{nextgems2023a,nextgems2023b} for a model
time period of 20 January 2020 to 22 July 2025, of which we analysed the full
years 2021--2024 (inclusive). While a Cycle 4 run was available, we could not
use due it to the unavailability of the necessary variables. The horizontal
resolution of ngc3028 is about 5 km.  The model output is available on 90
vertical levels and 3-hourly instantaneous temporal resolution.  Unlike current
general circulation models (GCMs), the strom-resolving version of ICON does not
use convective and cloud parameterisation but relies on explicit simulation of
convection and clouds on the model grid. While this makes the code development
simpler without having to rely on uncertain parameterisations, it can miss
smaller-scale clouds below the grid resolution.  Turbulence and cloud
microphysics are still parameterised in this model.

Because the model is free-running, weather and climate oscillations (such as
the El Niño--Southern Oscillation) are not expected to be equivalent to reality
at the same time and place. To compare with the observations collected on
different years (2010--2021, inclusive), we compared the model output with
observations at the same time of year and geographical location, as determined
for each data point such as a lidar profile or a radiosonde launch.

@@

The Modern-Era Retrospective analysis for Research and Applications, Version 2
(MERRA-2) is a reanalysis produced by the Global Modeling and Assimilation
Office at the NASA Goddard Space Flight Center \citep{gelaro2017}.  It uses
version 5.12.4 of the Goddard Earth Observing System (GEOS) atmospheric model
\citep{rienecker2008,molod2015}. The reanalysis output analysed here is
available at a spatial resolution of 0.5° of latitude and 0.625° of longitude,
which is about 56 km in the North--South direction and 35 km in the East--West
direction at 60°S. The number of vertical model levels is 72. Here, we use the
following products: 1-hourly instantaneous 2D single-level diagnostics
(M2I1NXASM) for 2-m temperature and humidity; 3-hourly instantaneous 3D
assimilated meteorological fields (M2I3NVASM) for cloud quantities, pressure,
and temperature; 1-hourly average 2D surface flux diagnostics (M2T1NXFLX) for
precipitation and sea ice; and 1-hourly average 2D radiation diagnostics
(M2T1NXRAD) for radiation quantities \citep{merra2}.

@@

ERA5 \citep{era5} is a reanalysis produced by the European Centre for
Medium-Range Weather Forecasts (ECMWF). It is based on a numerical weather
prediction (NWP) model Integrated Forecast System (IFS) version CY41R2.  The
horizontal resolution is 0.25° in latitude and longitude, which is about 28 km
in the North--South direction and 14 km in the East--West direction at 60°S.
Internally, the model uses 137 vertical levels. Here, we use output at 1-hourly
instantaeous time intervals, except for radiation quantities, which are
accumulations (from these we calculate daily means).  Vertically-resolved
quantities are made available on 37 pressure levels.

@@

Radiation calculations presented in the results (Section \ref{sec:results})
were done in such a way that they always represent averages of daily means.
This is done in order to be consistent with the CERES SYN1deg data, which are
available as daily means. Therefore, every instantaneous profile in the
simulated lidar data is assigned a daily mean radiation value corresponding to
the day (in the Coordinated Universal Time; UTC). In turn, the average
radiation during the entire voyage or station observation period is calculated
as the average of the profile values. In the observed lidar data, the daily
mean radiation value is taken from the spatially and temporally co-located
CERES SYN1deg data of the day (in UTC). The voyage or station average is
calculated in the same way.

@@

\subsection{Partitioning by cyclonic activity and stability}

In addition to the above, we partitioned our data into two subsets by
stability. We determined this by calculating lower tropospheric stability (LTS)
as the difference between the potential temperature at 700 hPa and the surface.
Based on a histogram of LTS in ERA5 and MERRA-2 calculated at all voyage tracks
and stations (Fig.  \ref{fig:lts}), we determined a dividing threshold of 12 K
for relatively unstable (< 12 K) and relatively stable (>= 12 K) conditions.
